Verified Time Balancing of Security Protocols \\ \large A Case Study

### 2018-12-18 Src/paper.tex
Need to look into MAC and HMAC in order to properly determine hasing for DH-Part 2
Some more work on DH

@@

        \item Let $pvi = mod(g^{svi},p)$
        \item Let $||$ denote bitwise concatenation

@@

  test
  \section{The DH Part 2 Message}

>>>>

    %TODO: Figure out what m actually does.

@@

        \item Let $pvi = mod(g^{svi},p)$.
        \item Let $||$ denote bitwise concatenation.

@@

  $alice_4(p_{b4},h2_{b4},z_{b4},ha_{b4},ca_{b4},at_{b4},kt_{b4}
    ,st_{b4},hvi_{b4},m_{b4})$
  \section{The DH Part 1 Message}
    \item Let $rstr$ represent a message denoting ``Responder''.
    \item Let $s1r$ represent the responders first shared secret
          if it exists, or null otherwise.
    \item Let $s2r$ represent the responders second shared secret
          if it exists, or null otherwise.
    \item Let $rs1r = m(s1r,rstr)$ represent the non-invertible 
          hash of the responders first retained shared secret.
    \item Let $rs2r = m(m2r,rstr)$ represent the non-invertible
          hash of the responders second retained shared secret.
    \item Let $auxr$ represent the responders auxiliary shared 
          secret.
    \item Let $rh3$ represent the responder H3 value.
    \item Let $asr = m(aux,rh3)$ represent the non-invertible hash
          of the responders auxiliary shared secret.
    \item Let $pbxr$ represent the responders pbx shared secret.
    \item Let $psr = m(pbx,rstr)$ represent the non-invertible
          hash of the responders pbx shared secret.
    \item Let $pvr$ represent the responders hash value where:
        \item Let $svr$ represent a random number.
        \item $svr$, $g$, and $p$ are all functions of $kt$
        \item Let $pvr = mod(g^{svr},p)$.
        \item Let $||$ denote bitwise concatenation.

  \section{The DH Part 2 Message}
  \begin{itemize}
    \item Let $istr$ represent a message denoting ``Initiator''.
    \item Let $s1$ represent the initiators first shared secret if
          it exists or null otherwise.
    \item Let $s2$ represent the initiators second shared secret if
          it exists or null otherwise.
    \item Let $rs1 = m(s1,istr)$ represent the non-invertible hash 
          of the initiators first retained shared secret.
    \item Let $rs2 = m(s2,istr)$ represent the non-invertible hash
          of the intiators second retained shared secret.
    \item Let $aux$ represet the auxiliary shared secret.
    \item Let $ih3$ represent the initiators H3 value.
    \item Let $asi = m(aux,ih3)$ represent the non-invertible hash
          of the initiators auxiliary shared secret.
    \item Let $pbx$ represent the pbx shared secret.
    \item Let $psi = m(pbx,istr)$ represent the non-invertible
          hash of the initiators pbx shared secret.
